Verifying Demonstrations

### 2021-06-17 paper/protocol-trusted.tex
Minor clarification for trusted protocol intro

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
  Anyone can do this.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs of participation to protesters.
  The proofs are constructed such that they are verifiable by third parties.
  The witness must be trusted by the verifier.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

Anyone can be a verifier (we required universal verifiability, 
\cref{desired-properties}).
The verifier defines the protest to be counted by setting the cause, time 
(interval) and location (area), \cf \cref{DefProtest}.
Now the verifier counts all proofs that verify correctly and fulfils the cause, 
time and location criteria.
The verifier can publish, \eg in a news paper, the final count together with 
the cause, time and location and anyone can verify this count (by the same 
procedure).

>>>>

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
  Anyone can do this, but in general, there is only one organizer.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs of participation to protesters.
  The proofs are constructed such that they are verifiable by third parties.
  The witness must be trusted by the verifier.
\end{enumerate}
Anyone can be a verifier (we required universal verifiability, 
\cref{desired-properties}).
The verifier defines the protest to be counted by setting the cause, time 
(interval) and location (area), \cf \cref{DefProtest}.
Now the verifier counts all proofs that verify correctly and fulfils the cause, 
time and location criteria.
The verifier can publish, \eg in a news paper, the final count together with 
the cause, time and location and anyone can verify this count (by the same 
procedure).
